Governing through patronage: the bargain for education in decentralized Brazil

### 2020-10-05 paper/paper.tex
push plots

Across the world, vulnerable populations rely on governments for access to basic public services such as education. In the developing world, the quality of public education remains low: functional illiteracy is widespread, basic mathematical operations beyond the reach of most \citep{vegas_raising_2007}. The World Bank refers to as ``learning poverty'': low gains from education even when access to a public school exists, in contrast with earlier focus on access to education.\footnote{For more information, see \hyperlink{here}{https://www.worldbank.org/en/topic/education/brief/learning-poverty}.} These outcomes are the end-result of a series of interlocking steps: from personnel decisions to service provision \citep{pepinsky_bureaucracy_2017}, each link in this institutional chain of command connects political principals to the child sitting in the classroom.

>>>>

Across the world, vulnerable populations rely on governments for access to basic public services such as education. In the developing world, the quality of public education remains low: functional illiteracy is widespread, basic mathematical operations beyond the reach of most \citep{vegas_raising_2007}. The World Bank refers to as ``learning poverty'': poor learning when access to a schooling already exists.\footnote{For more information, see \hyperlink{here}{https://www.worldbank.org/en/topic/education/brief/learning-poverty}.} As scholarly focus shifts from public service provision \citep{kaufman_globalization_2001, } to the quality

Raises two related questions. The first one concerns the relationship between the quality of public services and the structure of the bureaucracy \citep{pepinsky_bureaucracy_2017, rasul2018management}.

These outcomes are the end-result of a series of interlocking steps: from personnel decisions to service provision \citep{pepinsky_bureaucracy_2017}, each link in this institutional chain of command connects political principals to the child sitting in the classroom.
